\Title

### 2021-04-29 latex/paper/main.tex
Revamped the simulation and experimental sections, still lots to do

%---------- More packages ----------%
% NOTE: cannot use amsthm for some reason
\usepackage{mathtools}
\usepackage{bm}

@@

%/========== Acrobot ==========/%
\section{The Acrobot VNHC}\label{sec:acrobot}
%specialize the theory of VNHCs to the acrobot. consider constraints which depend
%only on pu, and show arctan vnhc and reduced dynamics. 
%give definition of energy injection/dissipation. conclude with our
%theorem. Make this section short and sweet.
%
%TODO: after writing S2, re-introduce what we want to do with acrobot (energy
%injection for giant stabilization)
Our goal in this article is to design a VNHC which injects energy into the
acrobot through giant-like motion.
Recall that the acrobot in Figure \ref{fig:simple-acrobot-model} has dynamics given by
~\eqref{eqn:acrobot-hamiltonian}, which are
repeated here:
\begin{align*}
    \mathcal{H}(q,p) &= \frac{1}{2}p\tpose \Minv(q) p -
    mgl\left(2 c_u + c_{ua}\right)
    , \\
     &\begin{cases}
        \dot{q} = \Minv(q) p 
        ,\\
        \dot{p}_u = -mgl\left(2s_u + s_{ua}\right) 
        ,\\
        \dot{p}_a =-\frac{1}{2}p\tpose \nabla_{q_a}\Minv(q) p
        - mgl s_{ua} + \tau.
    \end{cases}
\end{align*}

@@

%/========== Experiments ==========/%
\section{Simulation Results}\label{sec:simulations}
\textbf{TODO: simulation parameters in a table, show results for injection,
dissipation, and regulation along with existing simulations. Ample commentary.}

\section{Experimental Results}\label{sec:experiments}
\textbf{TODO: 2 sections. a) is hardware description, paraphrasing Xingbo.
    Should be brief but detailed (eg 2 arduinos, 3d printed, battery in the leg,
    parameters of the system, etc). b) is
experimental results, same as simulation section.}
We tested our VNHC on the physical acrobot built by
Xingbo Wang \cite{xingbo_thesis} (Figure \ref{fig:xingbo-acrobot}).
The torso and legs on this robot have differing masses and lengths, so
its inertia matrix and potential function are \textbf{not} described by 
~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

@@

For our VNHC to inject energy, we know the control parameter \(I\) must be small
(as per Theorem \ref{thm:acrobot-energy-stabilization}), but it must also be
large enough to overcome friction in leg motor.
Setting \(\bar{q}_a = 1\), we experimentally determined that \(I = 10\) is
sufficient to ensure the actuator can fully rotate in its allowable range \(q_a
\in \left[ -\frac{\pi}{2}, \frac{\pi}{2}\right]\). 
This is the value of \(I\) we used in all simulations and experiments.

\subsection{Simulations Results}
Evaluating the true mechanical energy of Wang's acrobot at the VNHC
\(q_a = 0\) yields the energy of the nominal pendulum,
\[
    E(q_u,p_u) \approx 396.5501 p_u^2 + 0.5997(1 - \cos(q_u))
    .
\]
We simulated Wang's acrobot with initial condition
\((q_u,p_u) = \left(\pi/32,0 \right)\) and plotted the resulting orbit
in Figure \ref{fig:acrobot-orbit}.

\begin{figure}[]
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_orbit.png}
    \caption{A simulated orbit of Wang's acrobot.}
    \label{fig:acrobot-orbit}
\end{figure}
To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured the how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

\subsection{Physical Experiments}

Wang's acrobot has an encoder which measures \(q_u\) and
\(\dot{q}_u\).
Additionally, the leg actuator is a servo motor with a built-in PID controller
which provides measurements of \(q_a\).
To implement our VNHC, we estimated \(\dot{q}_a\) through sequential values of
\(q_a\) and computed \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We directly assigned the actuator setpoint at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(10 p_u^{k-1})\).
We then performed the following tests.

>>>>

%---------- More packages ----------%
% NOTE: cannot use amsthm for some reason
\usepackage{mathtools}
\usepackage{bm}
\usepackage{booktabs}

@@

%/========== Acrobot ==========/%
\section{The Acrobot VNHC}\label{sec:acrobot}

Our goal in this article is to design a VNHC which injects energy into the
acrobot through giant-like motion.
Recall that the acrobot in Figure \ref{fig:simple-acrobot-model} has dynamics given by
~\eqref{eqn:acrobot-hamiltonian}, which are
repeated here:
\begin{align*}
    \mathcal{H}(q,p) &= \frac{1}{2}p\tpose \Minv(q) p -
    mgl\left(2 c_u + c_{ua}\right)
    , \\
     &\begin{cases}
        \dot{q} = \Minv(q) p 
        ,\\
        \dot{p}_u = -mgl\left(2s_u + s_{ua}\right) 
        ,\\
        \dot{p}_a =-\frac{1}{2}p\tpose \nabla_{q_a}\Minv(q) p
        - mgl s_{ua} + \tau.
    \end{cases}
\end{align*}

@@

%/========== Experiments ==========/%
\section{Simulation Results}\label{sec:simulations}
In Section \ref{sec:experiments} we will test our VNHC on the physical acrobot
built by Xingbo Wang \cite{xingbo_thesis} (Figure \ref{fig:xingbo-acrobot}).
To compare apples to apples, we will simulate our VNHC using the parameters of
the physical system (Table \ref{tab:acrobot-parameters}).

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_model.pdf}
    \caption{The general acrobot model, represented by two weighted rods
    differing in both length and mass.}%
    \label{fig:acrobot-model}
\end{figure}

\begin{table}
    \centering
    \caption{Physical parameters for the real acrobot.}
    \label{tab:acrobot-parameters}
    \resizebox{\columnwidth}{!}{%
    \begin{tabular}{ccccccccc}
        \toprule
        $m_u$ & $m_a$ & $l_u$ & $l_a$ & $l_{c_u}$ & $l_{c_a}$ & $J_u$ & $J_a$ & $g$ \\
        \midrule
        0.2112 & 0.1979 & % mass
        0.148 & 0.145 & % total length
        0.073 & 0.083 & % COM distance
        0.00129 & 0.00075 & % moment of inertia
        9.81 \\ % gravity
        \bottomrule
    \end{tabular}
    } % resizebox
\end{table}

Note that these parameters do not correspond to our simplified acrobot in Figure
\ref{fig:simple-acrobot-model}, but rather to the more general acrobot model in
Figure \ref{fig:acrobot-model}.
In particular, the inertia matrix and potential function are \textbf{not}
described by ~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
The correct \(M(q)\) and \(V(q)\) can be found in Wang's thesis
\cite{xingbo_thesis}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

Evaluating the true mechanical energy of this acrobot at the VNHC
\(q_a = 0\) yields the energy of the nominal pendulum,
\[
    E(q_u,p_u) \approx 396.5501 p_u^2 + 0.5997(1 - \cos(q_u))
    .
\]

According to Theorem \ref{thm:acrobot-energy-stabilization}, the control
parameter \(I\) must be small.
While we could choose \(I\) arbitrarily small in simulations, we will eventually
compare these simulations with the physical experiments where \(I\) must be
large enough to overcome friction in leg motor.
Setting \(\bar{q}_a = 1\), we experimentally determined that \(I = 10\) is a
viable control value.
This is the value of \(I\) we used in all simulations and experiments.

\textbf{TODO: the injection and dissipation I is different, so we might not use
I = 10 for dissipation.}

\subsection{Energy Injection}

To validate the energy injection property of our VNHC, we simulated the acrobot
with initial condition \((q_u,p_u) = \left(\pi/32,0 \right)\) and plotted the
resulting orbit in Figure \ref{fig:acrobot-orbit}.

\begin{figure}[]
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_orbit.png}
    \caption{A simulation of the acrobot gaining energy.}
    \label{fig:acrobot-orbit}
\end{figure}

To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured the how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

\subsection{Energy Dissipation}

\subsection{Energy Regulation}

\section{Physical Experiments}\label{sec:experiments}

@@

\subsection{Hardware Description}
\textbf{TODO: paraphrase xingbo. 2 arduinos, 3d printed, battery in leg,
parameters of system, etc}

\subsection{Experimental Results}

\textbf{TODO: rework this section. In simulation we showed that we gain energy
continuously. Here we only gain energy up to speed 0.195 because of friction.}
Wang's acrobot has an encoder which measures \(q_u\) and
\(\dot{q}_u\).
Additionally, the leg actuator is a servo motor with a built-in PID controller
which provides measurements of \(q_a\).
To implement our VNHC, we estimated \(\dot{q}_a\) through sequential values of
\(q_a\) and computed \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We directly assigned the actuator setpoint at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(10 p_u^{k-1})\).
We then performed the following tests.
